---
title: "Climate Response Host NonHost"
author: "A Hessl"
date: "5/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(dplR)
library(treeclim)
library(lubridate)
```
### Read in the chronologies
I've tried to make this adaptable for when you have lots of chronologies to read in. You should be able to make a function whose argument is "site". If you have a folder that has 3 files for each site that have a site prefix and either a crn.txt or monthly.csv suffix, we should be able to apply over all of them.

```{r read chrons}
site <- 'UPT'
host <- 'ABBA'
nonhost <- 'PCRU'
h_path <- paste0("data/chronologies/", site, "_", host, "_crn.txt")
h_crn <- read.table(h_path)

n_path <- paste0("data/chronologies/", site, "_", nonhost, "_crn.txt")
nh_crn <- read.table(h_path)
```

### Read in the climate data
Adjust for treeclim format required
```{r read climate}

monthly <- "_monthly.csv"
clim.path <- paste0("data/climate_data/", site, monthly)
monthly_dat <- read.csv (clim.path, skip=11, head=F)
    
climvars <- c("pdate", "ppt", "tmin", "tmean", "tmax")
monthly_dat <- setNames(monthly_dat, climvars)
   
#Arrange with year, month, data cols for treeclim 
monthly_dat$pdate <- paste0(monthly_dat$pdate, "-01")
year <- year(monthly_dat$pdate)
month <- month(monthly_dat$pdate)
monthly_dat <- cbind(year, month, monthly_dat[,-1])

#Remove incomplete years (2018)
monthly_dat <- monthly_dat[year!=2018,]
```

### Response Function in treeclim
w/bootstrapped confidence intervals
```{r dcc calib}
resp <- dcc(h_crn, monthly_dat, method="correlation", 
            ci = 0.01, selection=6:9, timespan=c(1959, 2010), win_size= 50, boot="exact") 
```

```{r plot calib resp}
#Extract one climate data variable to plot
coef.cal <- resp$coef[,c(3:5)]



pdf("products/climResponseCalib.pdf", width=4, height=3)
palette(c("white", "grey30"))
barplot(coef.cal$coef, width=1, names.arg=row.names(coef.cal), las=2, col=factor(coef.cal$significant), ylim=c(0,0.5), ylab="Cor Coef", main="Climate Response (1959-2010)")
dev.off()
```